Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
improved the big table

\begin{tabular}{ccc}\toprule
  \begin{tabular}{c}
    \code{[7\, 0\, 2]}$\to $\code{[2\, 0\, 7]} \\
      \code{[2\, 4\, 9\, 3]}$\to $\code{[3\, 9\, 4\, 2]}\\
      \code{$f(x) = $}\code{($f_0$ nil)}\\\\
      \code{[99\, 4\, 2]}$\to $\code{99}\\
      \code{[2\, 1\, 4\, 6]}$\to $\code{6}\\
      \code{[8\, 7\, 7\, 7]}$\to $\code{8}\\
      \code{($f_1$ )}
  \end{tabular}&
  \begin{tabular}{c}
    +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
    +83 973-831$\to $83.973.831\\
    $f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,} ($f_0$ \codechar{.} \codechar{ } (cdr s)))}    \\\\
Temple Anna H $\to $TAH\\
Lara Gregori$\to $LG\\
$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}\\

@@

  \begin{tabular}{c}
    \includegraphics[width = 1cm]{figures/functions/4.png}\\
    \code{$f($x$) = $($f_1$ -0.8 1.6)}\\
    \includegraphics[width = 1cm]{figures/functions/112.png}\\
    \code{$f($x$) = $($f_0$ -0.8 1.6)}\\

@@

  \\\midrule&

  \begin{tabular}{l}
          $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x) (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty? car ($\lambda$ (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words})\\
    \end{tabular}&

  \begin{tabular}{l}
    $f_0($\code{x}$)\,=\,$\code{(+ x real)}\quad
  $f_1($\code{x}$)\,=\,$\code{($f_0$ (* real x))} \\
  $f_2($\code{x}$)\,=\,$\code{($f_1$ (* x (}$f_0$\code{ x)))}\\
    \end{tabular}

@@

>>>>

\begin{figure}[hb]
\makebox[\textwidth][c]{
\scriptsize
\renewcommand\code\texttt
\renewcommand\codechar[1]{\texttt{"#1"}}
\begin{tabular}{>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}}\toprule
  Lists&Strings&Symbolic Regression\\\midrule
  \begin{tabular}{c}
      % \code{[7\, 0\, 2]}$\to $\code{[2\, 0\, 7]} \\
      % \code{[2\, 4\, 9\, 3]}$\to $\code{[3\, 9\, 4\, 2]}\\
      % \code{$f(x) = $}\code{($f_0$ nil $x$)}\\\\
      \code{[99\, 4\, 2]}$\to $\code{99}\\
      \code{[2\, 1\, 4\, 6]}$\to $\code{6}\\
      \code{[8\, 7\, 7\, 7]}$\to $\code{8}\\
      \code{$f(\ell) = $}\code{($f_0$ $\ell$)}\\\\
      \code{[7\, 3\, 14\, 6\, 9]}$\to $\code{false}\\
      \code{[9\, 4\, 3\, 4]}$\to $\code{true}\\
      \code{$f(\ell) = $}\code{($f_1$ $\ell$ k)}
  \end{tabular}&
  \begin{tabular}{c}
    +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
    +83 973-831$\to $83.973.831\\
    $f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,} ($f_0$ \codechar{.} \codechar{ } (cdr s)))}\\\\
Temple Anna H $\to $TAH\\
Lara Gregori$\to $LG\\
$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}\\

@@

  \begin{tabular}{c}
    \includegraphics[width = 3em]{figures/functions/4.png}\\
    \code{$f($x$) = $($f_1$ -0.8 1.6)}\\
    \includegraphics[width = 3em]{figures/functions/112.png}\\
    \code{$f($x$) = $($f_0$ -0.8 1.6)}\\

@@

  \\\midrule

  \begin{tabular}{l}
    % $f_0($\code{r}$,\ell) \,=\, $\code{(fold $\ell$ r ($\lambda$ (x a)}\\
    % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(fold}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{0.5cm}($f_1$: \emph{Get the largest number})\\
    $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a) (if (> a x) a x)))}\\
      \hspace{0.5cm}($f_1$: \emph{Get the largest number in $\ell$})\\
    $f_1(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (empty$?$ $\ell$)}\\
    \phantom{$f_1(\ell,$\code{k}$) \,=\, $\code{(foldr}}
    \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{0.5cm}($f_1$: \emph{Whether $\ell$ contains $k$})\\
  \end{tabular}&

  \begin{tabular}{l}
          $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x) (if (= x a) b x)) s)}\\
      \hspace{0.5cm}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty$?$ car ($\lambda$ (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words})\\
    \end{tabular}&

  \begin{tabular}{l}
    $f_0($\code{x}$)\,=\,$\code{(+ x real)}\\
  $f_1($\code{x}$)\,=\,$\code{($f_0$ (* real x))} \\
  $f_2($\code{x}$)\,=\,$\code{($f_1$ (* x (}$f_0$\code{ x)))}\\
    \end{tabular}

@@

\end{tabular}}
\end{figure}
